### 2023-05-10 chapter2/chapter2.tex
Added first paragraph of discussion

\section{Discussion}
% I. Summary of results
%    A. In this study, we applied several phylogenetic models to IDRs to interrogate the evolution of their sequences and molecular features.
%    B. Most significantly, we demonstrate evidence of widespread evolutionary constraint in IDRs within the \textit{Drosophila} proteome
%    C. Furthermore, many IDRs can be grouped into discrete clusters on the basis of these evolutionary signatures
%    B. Most immediately, this work generates hypotheses of function related to sequence features that will permit the functional dissection of IDRs
%    C. More broadly, however, it illustrates constraint of distributed features characterizes the evolution of some IDRs across multiple systems.
%    D. However, these clusters require careful interpretation. The cluster descriptions summarize only a subset of the annotations with statistically significant enrichments. All clusters had many enriched annotations, but the summaries correspond to sets of enrichments with consisten . Because the significance tests were not corrected for multiple testing or controlled for their false discovery rate, many annotations are ,

\subsection{IDRs have distinct patterns of sequence and feature evolution}
In addition to these global clusters of conserved features, we find IDRs are characterized by other distinct patterns of evolution. For example, a comparison of the exchangeability matrices fit to the disorder and order regions shows that, relative to the order regions, the disorder regions have decreased exchangeability coefficients between the disorder-enriched residues. Conversely, the disorder-depleted residues have increased exchangeability coefficients with each other. As a residue's enrichment in IDRs is generally interpreted as a measure of its ability to promote intrinsic disorder, these results indicate that within IDRs and relative to folded domains, disorder-promoting residues are subject to stricter constraints whereas structure-promoting residues are more biochemically interchangeable. A potential weakness of this analysis is its dependence on sequence alignments which were created using scoring matrices that are in turn derived from other substitution models. Previous studies have attempted to minimize the impact of this circular dependency through an EM-like procedure where substitution models are first fit to alignments, and the sequences in the alignments are then re-aligned with scoring matrices derived from the fit models in alternating rounds until convergence~\cite{Brown2009, Szalkowski2011}. Because our analyses fit the substitution models directly from alignments, the observed patterns are possibly an artifact of using a scoring matrix derived from folded domains to align IDRs. However, as our matrices reproduce the trends reported in these prior studies, they likely reflect true differences in the patterns of residue substitution within IDRs.

>>>>

\section{Discussion}
\subsection{IDRs have distinct patterns of sequence and feature evolution}
In this study, we applied several phylogenetic models to IDRs to interrogate the evolution of their sequences and molecular features. Most significantly, through a comparison of two models of continuous trait evolution we demonstrate evidence of widespread constraint in IDRs within the \textit{Drosophila} proteome. Furthermore, using evolutionary signatures derived from these models, we identify several clusters of IDRs with shared patterns of constraint and associations with specific biological functions. Most immediately, this work generates hypotheses on the importance of various molecular features that will aid in the functional dissection of IDRs in specific proteins. More broadly, though, it suggests that constraint of distributed features is a mechanism of IDR evolution common to multiple biological systems. However, in the absence of more detailed analyses of individual clusters, it remains unclear if any are homologous or analogous to those identified in yeast. Additionally, the clusters' functional associations require careful interpretation. For example, the cluster descriptions summarize a subset of the enriched annotations which were selected for their related functions. Because the significance tests were not corrected for multiple testing or controlled for their false discovery rate, some annotations with significant enrichment, which may include the subset selected for the cluster descriptions, are likely spurious. Thus, while these initial results are promising, further investigation is necessary to corroborate them.

In addition to these global clusters of conserved features, we found IDRs exhibit other distinct patterns of evolution. For example, a comparison of the exchangeability matrices fit to the disorder and order regions shows that, relative to the order regions, the disorder regions have decreased exchangeability coefficients between the disorder-enriched residues. Conversely, the disorder-depleted residues have increased exchangeability coefficients with each other. As a residue's enrichment in IDRs is generally interpreted as a measure of its ability to promote intrinsic disorder, these results indicate that within IDRs and relative to folded domains, disorder-promoting residues are subject to stricter constraints whereas structure-promoting residues are more biochemically interchangeable. A potential weakness of this analysis is its dependence on sequence alignments which were created using scoring matrices that are in turn derived from other substitution models. Previous studies have attempted to minimize the impact of this circular dependency through an EM-like procedure where substitution models are first fit to alignments, and the sequences in the alignments are then re-aligned with scoring matrices derived from the fit models in alternating rounds until convergence~\cite{Brown2009, Szalkowski2011}. Because our analyses fit the substitution models directly from alignments, the observed patterns are possibly an artifact of using a scoring matrix derived from folded domains to align IDRs. However, as our matrices reproduce the trends reported in these prior studies, they likely reflect true differences in the patterns of residue substitution within IDRs.
